visualFields 1.x

### 2025-05-09 vignette.Rmd
Start des jstatsoft-Artikels.

To install the released version of the package, run 
```{r eval=FALSE}
install.packages("visualFields")
```

To install the newest version of the package, run:
```{r eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("imarinfr/vf1/source")
```

To load the package run
```{r}
library(visualFields)
```

>>>>

To install the released version of the package, run 
```{r install from CRAN, eval=FALSE}
install.packages("visualFields")
```

To install the newest version of the package, run:
```{r install from github, eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("imarinfr/vf1/source")
```

To load the package run
```{r load package}
library(visualFields)
```
